### 2013-09-25 manuscripts/dpp-msbayes/dpp-msbayes.tex
More work on methods of dpp ms.

@@

\subsection*{The ABC implementation of the model}

>>>>

\highLight{Need to discuss units of time and how they are scaled from units
    proportional to time to units proportional to mutations.}

@@

\subsection*{The ABC implementation of the model}
To estimate the approximate posterior of Equation \ref{eq:approxModelCompact},
we use an ABC rejection algorithm.
The first step of this algorithm entails collecting a random sample of
parameters values from the joint prior and their associated summary
statistics.
Each sample is generated by
(1) drawing values of all the model's parameters \hpvector{} from their respective
prior distributions,
(2) rescaling the divergence times in \divTimeMapVector from units
proportional to time to units proportional to the expected number
of mutations via Equation X,
(3) simulate a gene tree by drawing coalescent times from
a multi-population Kingman-coalescent model,
(4) simulating sequences along the gene tree under the
\hky substitution parameters of \hkyModelVector,
and (5) calculating population genetic summary statistics from the sequences
\ssVector{} (these are the same statistics calculated from the observed
alignments, \ssVectorObs{}).
